Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
fix

pollster_summary <- harrisdata %>%
  group_by(end_date_num) %>%
  summarize(
    mean_support = mean(pct, na.rm = TRUE),
    median_support = median(pct, na.rm = TRUE),
    lower_quartile = quantile(pct, 0.25, na.rm = TRUE),
    upper_quartile = quantile(pct, 0.75, na.rm = TRUE)
  )

@@

In states like Arizona, Georgia, Michigan, and North Carolina, the model predicts a steady increase in support for Harris over time, as shown in @fig-modelGAWM.
In states such as Nevada, Pennsylvania, and Wisconsin, the model predicts a decline in support over time, as seen in @fig-modelNPW.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modelGAWM
#| fig-cap: "Poll predictions of Arizona, Geogria, Michigan, North Carolina"

>>>>

pollster_summary <- harrisdata %>%
  group_by(end_date_num) %>%
  summarize(mean_support = mean(pct, na.rm = TRUE),
    median_support = median(pct, na.rm = TRUE),
    lower_quartile = quantile(pct, 0.25, na.rm = TRUE),
    upper_quartile = quantile(pct, 0.75, na.rm = TRUE))

@@

In states like Arizona, Georgia, Michigan, and North Carolina, the model predicts a steady increase in support for Harris over time, as shown in @fig-modelGANM.
In states such as Nevada, Pennsylvania, and Wisconsin, the model predicts a decline in support over time, as seen in @fig-modelNPW.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modelGANM
#| fig-cap: "Poll predictions of Arizona, Geogria, Michigan, North Carolina"
